multiple_sig_sample

### 2021-06-23 manual_classification.Rmd
Finished manual implementation of classification

df.final <- data.frame(append(sample.sig6, sample.ffpe), append(sig6.truth, ffpe.truth))
df.final
```

@@

for (x in mutations) {
  probs <- extract_all_prob(x, 1, nmf_res)
  print(x)
  print(probs)
  mmr.prob <- c(mmr.prob, probs$MMR)
  ffpe.prob <- c(ffpe.prob, probs$FFPE)
}

mmr.prob
ffpe.prob
```

>>>>

df.final <- data.frame(append(sample.sig6, sample.ffpe), append(sig6.truth, ffpe.truth))
colnames(df.final) <- c("mutations", "truth")
```

@@

for (x in mutations) {
  probs <- extract_all_prob(x, 1, nmf_res)
  mmr.prob <- c(mmr.prob, probs$MMR)
  ffpe.prob <- c(ffpe.prob, probs$FFPE)
}

df2 <- data.frame(mutations, mmr.prob, ffpe.prob)
df2

df.final <- left_join(df.final, df2, by = "mutations")

df.final <- df.final %>%
  mutate(
    classify = ifelse(mmr.prob > ffpe.prob, "MMR", "FFPE"),
    missClassification = ifelse(truth != classify, 1, 0)
  )

mean(df.final$missClassification)
```
